%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{filemod}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\def\parsedate #1:20#2#3#4#5#6#7#8\empty{20#2#3/#4#5/#6#7}
\def\moddate#1{\expandafter\parsedate\pdffilemoddate{#1}\empty}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf \href{https://www.thomasboudreaux.com}{Thomas M. Boudreaux}} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{19 Drake Lane} % Your address
\moveleft.5\hoffset\centerline{West Lebanon, New Hampsire 03784}
\moveleft.5\hoffset\centerline{(571)-428-8828}
\moveleft.5\hoffset\centerline{thomas@boudreauxmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Areas of Interest SECTION
%----------------------------------------------------------------------------------------
 
\section{RESEARCH INTERESTS}  
Computational astrophysics, stellar evolution, machine learning, pulsating hot subluminous B stars, chaotic systems.
 

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{EDUCATION}
{\large Dartmouth College} \hfill Hanover, NH\\
{\-\ \-\ \small \textit{Master of Science} --- Astronomy} \hfill May 2022\\
{\-\ \-\ \-\ \-\ \small Advisor: \href{https://physics.dartmouth.edu/people/brian-charles-chaboyer}{Brian C. Chaboyer}} \\
{\-\ \-\ \-\ \-\ \small Secondary Advisor: \href{https://physics.dartmouth.edu/people/elisabeth-newton}{Elisabeth R. Newton}} \\
{\-\ \-\ \small \textit{Doctor of Philosophy} –-- Astronomy} \hfill Spring 2024 (expected)

{\large High Point University} \hfill High Point, NC\\
	{\-\ \-\ \small \textit{Bachelor of Science}, \textbf{summa cum laude} --- Computational Physics} \hfill May 2019\\
{\-\ \-\ \-\ \-\ \small Advisor: \href{http://linus.highpoint.edu/~bbarlow/}{Brad N. Barlow}} \\

\section{PUBLICATIONS}
\begin{itemize}
	\item \textbf{Boudreaux, T.M.}, Chaboyer, B.C., 2022. Updated High-Temperature Opacties for the Dartmouth Stellar Evolution Program and their Effect on the Jao Gap Location, \textit{The Astrophysical Journal}. \textbf{In. Pres.}
	\item \textbf{Boudreaux, T.M.}, Newton, E.R., Mondrik, N., Charbonneau, D., Irwin, J., 2021. \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...929...80B/abstract}{The Ca II H\&K Rotation-Activity Relation in 53 mid-to-late type M-Dwarfs}, \textit{The Astrophysical Journal}. 926(1), p.80
	\item Guidry, J.A., Vanderbosch, Z.P., Hermes, J.J., Barlow, B.N., Lopez, I.D., \textbf{Boudreaux, T.M.}, Corcoran, K.A., Bell, K.J., Montgomery, M.H., Heintz, T.M. and Castanheira, B.G., 2021. \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...912..125G/abstract}{I Spy Transits and Pulsations: Empirical Variability in White Dwarfs Using Gaia and the Zwicky Transient Facility.} \textit{The Astrophysical Journal}, 912(2), p.125.
\item Vos, J., Vu\u{c}kovi\`c, M., Chen, X., Han, Z., \textbf{Boudreaux, T. M.}, Barlow, B. N., \O stensen, R., N\`emeth, P., 2019, ``\href{https://ui.adsabs.harvard.edu/#abs/2019MNRAS.482.4592V/abstract}{The orbital period --- mass ratio relation of wide sdB+MS binaries and its application to the stability of RLOF.}", \textit{Monthly Notices of The Royal Astronomical Society}, \textbf{482}, 4592 
\item \textbf{Boudreaux, T. M.}, 2017, ``\href{https://ui.adsabs.harvard.edu/#abs/2017OAst...26..258B/abstract}{The applications of deep neural networks to sdBV classification}'', \textit{Open Astronomy}, \textbf{26}, 258.
\item \textbf{Boudreaux, T. M.}, Barlow, B. N., Fleming, S. W., Soto, A. V., Million, C., Reichart, D. E., Haislip, J. B., Linder, T. R., Moore, J. P., 2017. ``\href{https://ui.adsabs.harvard.edu/#abs/2017ApJ...845..171B/abstract}{A search for rapidly pulsating hot subdwarf stars in the GALEX survey}'', \textit{Astrophysical Journal}, \textbf{845}, 171.
\end{itemize}

\section{PROCEEDINGS}
\begin{itemize}
\item Vos, J., Vu\u{c}kovi\`c, M., Chen, X., Han, Z., \textbf{Boudreaux, T. M.}, Barlow, B. N., \O stensen, R., N\`emeth, P., 2019, ``\href{http://www.ta3.sk/caosp/Eedition/FullTexts/vol49no2/pp264-270.pdf}{Using wide hot subdwarf binaries to constrain Roche-lobe overflow models}", \textit{Contrib. Astron. Obs. Skalnaté Pleso}, \textbf{49}, 264 
\end{itemize}

\section{COMPUTING \\ SKILLS} 

\begin{itemize}
\item {\sl Programming Languages:} 
    \begin{enumerate}
        \item{\sl Expert: } Python, C/C++
        \item{\sl Comfortable: } Fortran 77/90/95, Arduino, PHP, JavaScript, Mathematica
        \item{\sl Familiar: } LabView, Go, Rust 
    \end{enumerate}
\item {\sl Web Backend Technologies:} Flask, MongoDB, MySQL, MariaDB
\item {\sl Misc:} Period04, Docker, GitHub, ZFS, LaTeX, Bash, Zsh
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 


\section{AWARDS \& HONORS}
\begin{itemize}
    \item \textbf{{\scriptsize The National Science Foundation}}, {\small 2019}\\Graduate Record Fellowship Program Honorable Mention
    \item \textbf{{\scriptsize High Point University}},
    {\small 2019}\\University Award for Highest Achievement
    \item \textbf{{\scriptsize High Point University Honors Scholar Program}},
    {\small 2019}\\All University Honors
	\item \textbf{{\scriptsize The Barry Goldwater Scholarship and Excellence in Education Foundation}}, {\small 2018}\\Goldwater Scholar in Mathematics, Science, and Engineering 
    \item \textbf{{\scriptsize High Point University Department of Physics}}, {\small 2018}\\Endowed Scholarship
    \item {\scriptsize \textbf{National Collegiate Honors Council}}, {\small 2018}\\Portz Scholarship
    \item \textbf{{\scriptsize Sigma Xi, The Scientific Research Honors Society}}, {\small 2018}\\Elected Associate Member
     \item \textbf{{\scriptsize Sigma Pi Sigma, National Physics Honor Society}}, {\small 2018}\\Elected Member
    \item \textbf{{\scriptsize The Barry Goldwater Scholarship and Excellence in Education Foundation}}, {\small 2017}\\Honorable Mention for excellence in Mathematics, Science, and Engineering 
	\item \textbf{{\scriptsize High Point University}}, {\small 2015--2019}\\Presidential Scholarship
\end{itemize}

\section{SELECTED ORAL\\PRESENTATIONS}
\begin{itemize}
	\item {\scriptsize \textbf{National Collegiate Honors Council Annual Meeting}}, {\small 2018, Boston, MA}\\ ``The Applications of Deep Neural Networks to sdBV Classification'' {\footnotesize [Invited]}
	\item {\scriptsize \textbf{North Carolina Astronomers Meeting}}, {\small 2017, Greensboro, NC}\\ ``The Applications of Deep Neural Networks to sdBV Classification''
	\item {\scriptsize \textbf{Eighth Annual Meeting on Hot Subdwarfs and Related Objects}}, {\small 2017, Krak\`ow, Poland}\\ ``The Applications of Deep Neural Networks to sdBV Classification''
	\item {\scriptsize \textbf{High Point University Research and Creative Works Symposium}}, {\small 2017, High Point, NC}\\ ``A Virtual Survey of all known Hot Subdwarfs -- searching for p-mode pulsations with GALEX''
	\item \textbf{{\scriptsize Meeting of Astronomers in South Carolina}}, {\small 2017, Greenville, SC}\\``The Applications of Deep Neural Networks to Time Domain Astrophysics''
\end{itemize}

\section{SELECTED POSTER\\PRESENTATIONS}
\begin{itemize}
	\item {\scriptsize \textbf{21st Meeting on Cool Stars}}, {\small 2022, Toulouse France}\\Updated High-Temperature Opacties for DSEP and Their Effect on the Jao Gap Location
	\item {\scriptsize \textbf{233rd Meeting of the American Astronomical Society}}, {\small 2019, Seattle Washington}\\ ``\href{https://ui.adsabs.harvard.edu/#abs/2019AAS...23314705C/abstract}{A Journey to Mars: HPUniverse Day and Its Impact on Young Minds and a Community.}''
	\item {\scriptsize \textbf{233rd Meeting of the American Astronomical Society}}, {\small 2019, Seattle Washington}\\ ``\href{https://ui.adsabs.harvard.edu/#abs/2019AAS...23324909B/abstract}{Effects of the Primordial Binary Fraction on the Evolution of Globular Clusters.}''
	\item \textbf{{\scriptsize 231st Meeting of the American Astronomical Society}}, {\small 2018, Washington D.C.}\\``\href{https://ui.adsabs.harvard.edu/#abs/2018AAS...23115029B/abstract}{Using Deep Learning to Analyze the Voices of Stars.}''
	% \item \textbf{{\scriptsize North Carolina Academy of Sciences Annual Meeting}}, {\small 2017, High Point, NC}\\ ``A Virtual Survey of all known Hot Subdwarfs -- searching for p-mode pulsations with GALEX''
	\item \textbf{{\scriptsize 227th Meeting of the American Astronomical Society}}, {\small 2016, Kissimmee, FL}\\``\href{https://ui.adsabs.harvard.edu/#abs/2016AAS...22734412B/abstract}{New Long Period Hot Subdwarfs from the Hobby-Eberly Telescope}''
\end{itemize}

\section{TEACHING EXPERIENCE}
\begin{itemize}
	\item {\scriptsize \textbf{Dartmouth College}}, {\small 2022} \\ Advanced Stellar Astrophysics (\textit{Astr 115})
	\item {\scriptsize \textbf{Dartmouth College}}, {\small 2021,2022} \\ Public Obsserving Teaching Assistant
	\item {\scriptsize \textbf{Dartmouth College}}, {\small 2020} \\ Introductory Mechanics Teaching Assistant (\textit{Phys 13})
	\item {\scriptsize \textbf{Dartmouth College}}, {\small 2020} \\ Introductory Solar System Astronomy (\textit{Astr 1})
\end{itemize}

\section{JOBS \& INTERNSHIPS}
\begin{itemize}
  \item \textbf{{\scriptsize Harvard Smithsonian Astrophysical Observatory}}, {\small 2018} \\Harvard SAO REU Student
  \item \textbf{{\scriptsize Space Telescope Science Institute}}, {\small 2016} \\SASP Summer Intern
\end{itemize}

\section{SOFTWARE}
All of my software can be found on my \href{https://github.com/tboudreaux}{GitHub} page.
\begin{itemize}
	\item \href{https://github.com/tboudreaux/pytopsscrape}{pyTOPSScrape} --- Custom python API for the Los Alamos OPLIB High-Temperature Opacties tables.
	\item \href{https://github.com/tboudreaux/mpl_animate}{mplEasyAnimate} --- Simple and easy animation library for use with matplotlib.
	\item \href{https://github.com/AstroSynth/astroSynth}{astroSynth} --- Synthetic pulsating star light curve generation suite.
	\item \href{https://github.com/tboudreaux/pyBJD}{pyBJD} --- Python bindings for Ohio state UTC to BJD conversion. [Deprecated]
	\item \href{https://github.com/tboudreaux/vectorpy}{vectorPy} --- Python 3--vector package.
\end{itemize}

\section{RESEARCH PROJECTS}
\begin{itemize}
	\item The Jao Gap width and location as a population age indicator, 2022-
	\item The effect of Opacties on the location of the Jap Gap, 2021-
	\item Modifying the Dartmouth Stellar Evolution Program to fully self consistantly handel increased He abundance, 2020-
	\item The Ca II H\&K Rotation-Activity Relation in 50 early-to-late type M-dwarfs, 2019-2020.
    \item Effects of the Primordial Binary Fraction on Globular Cluster Evolution, 2018
	\item Applications of Deep Learning to Classification of PTF Data, 2018
    \item Applications of Machine Learning to the Classification of Pulsating Stars, 2017--2018
    \item A Search for Rapidly Pulsating Hot Subdwarfs in the GALEX Survey, 2016--2017
    \item Orbital Solution Analysis of Long Period sdB+F/G/K Binaries, 2015--2016
\end{itemize}


\end{resume}
\end{document}
